PRT Appendix - 1

### 2023-09-27 _analysis/EcoConsPreReg-supervisor_draft-Sep-2020.Rmd
rename _analysis

This second activity aimed to identify critical challenges and roadblocks to the implementation and uptake of preregistration in ecology and conservation, as well as brainstorming solutions to these challenges. We conducted two lots of structured discussions, one for each of the field and modelling template groups. Each discussion was structured using a series of pre-prepared questions and talking points informed by recent debates about preregistration in the literature \<cite / link to OSF, or even discuss??\>. These talking points were chosen with the aim of identifying problems in the content and or structuring of the phases and decision steps that were collectively identified in activity 1, as well as any conceptual or philosophical issues with preregistration in ecology, conservation, and in particular modelling, that might impact on the template structure, content and procedural implementation of preregistration.

@@

A preliminary idealised scientific workflow for ecological modelling research was synthesised after reviewing the literature on 'good modelling practice' and structured decision-making literature in ecological management. Steps in the workflow were coded and broken down into 'phases' consisting of 'steps' and 'substeps', in line with the ontology we specified for translating a modelling workflow into a preregistration template [section link], \<insert link to appendices or just present the final?\>. Each decision-point in the personal modelling workflows generated from activity one of the collaborative workshop were coded as belonging to one of these phases, steps and substeps. We revised the coding structure \<inductively (is this the word)\>, according to patterns and themes identified across multiple personal workflows. For example, we added the final phase \<name for last phase\>, which aimed to capture the fact that analysts usually present the results of their modelling to clients, decision-makers or other stakeholders that must interpret the evidence and are responsible for making management decisions. In this way, we identified a common or generalised workflow from different types of applied ecological modelling projects that synthesised both \<idealised norms and norms of practice, Pu et al., see other philosophy of sci refs\>. This workflow is used to provide structure and content to the preregistration template.

@@

In order to address the disjuncture between the iterative nature of model development, and the single-use, deterministic preregistration template, we take an 'expanded view of preregistration', that fits with the concept of 'adaptive preregistration' proposed by \<Srivastava\>. This view of preregistration breaks with the current model of preregistration, wherein the author writes a single deterministic preregistration containing a rule for every decision, and shifts from ideation, preregistration to execution of the plan. Two features define adaptive preregistration. It contains 'plans to deploy flexible strategies' \<Srivastava\> wherein the author can supply a heuristic consisting of multiple different analysis or modelling strategies whose execution depends on the outcome of previous decision-points or analyses. Secondly, the preregistration may be iterative and consist of interim preregistrations that mark phases of modelling and analysis as different parts of the data are observed \<Srivastava\>. Thus, as the modeller proceeds through the model development process, the researcher can shift from ideation, preregistration, execution of the analysis and back to ideation and preregistration again, depending on the observed outcomes as each interim preregistration is executed \<Link to Figure, GitHub as a platform for adaptive preregistration, \<x-scrivener-item:///Users/egould/Dropbox/Apps/Scrivener/PhD_thesis.scriv?id=32FCFBDA-7CEE-4FD9-B8DD-F3073309C0D0\>\>.

@@

Before shifting from planning to the execution of the interim preregistration, each complete response in the interim preregistration should have a corresponding *GitHub issue* created (Figure X, step 3, document). \<define GitHub issue, <https://guides.github.com/features/issues/>\>. Relevant discussion between analysts about how to proceed with the intended analysis or interpreting preliminary results are tracked within an *issue*'s thread. Each issue is assigned a unique number. Any code or analysis outputs, such as figures, tables or other files, should be committed and tagged with the issue number, so that all analysis addressing that task is tracked within the *issue's* thread (Fig X, step 4, Do) \<screen-cap?\>. The URL for the GitHub issue should then be added to the relevant preregistration item, the preregistration document should then be committed with the changes, and the version number of the preregistration updated in a new *release*.

>>>>

This second activity aimed to identify critical challenges and roadblocks to the implementation and uptake of preregistration in ecology and conservation, as well as brainstorming solutions to these challenges.
We conducted two lots of structured discussions, one for each of the field and modelling template groups.
Each discussion was structured using a series of pre-prepared questions and talking points informed by recent debates about preregistration in the literature \<cite / link to OSF, or even discuss??\>
.
These talking points were chosen with the aim of identifying problems in the content and or structuring of the phases and decision steps that were collectively identified in activity 1, as well as any conceptual or philosophical issues with preregistration in ecology, conservation, and in particular modelling, that might impact on the template structure, content and procedural implementation of preregistration.

@@

A preliminary idealised scientific workflow for ecological modelling research was synthesised after reviewing the literature on 'good modelling practice' and structured decision-making literature in ecological management.
Steps in the workflow were coded and broken down into 'phases' consisting of 'steps' and 'substeps', in line with the ontology we specified for translating a modelling workflow into a preregistration template [section link], \<insert link to appendices or just present the final?\>
.
Each decision-point in the personal modelling workflows generated from activity one of the collaborative workshop were coded as belonging to one of these phases, steps and substeps.
We revised the coding structure \<inductively (is this the word)\>, according to patterns and themes identified across multiple personal workflows.
For example, we added the final phase \<name for last phase\>, which aimed to capture the fact that analysts usually present the results of their modelling to clients, decision-makers or other stakeholders that must interpret the evidence and are responsible for making management decisions.
In this way, we identified a common or generalised workflow from different types of applied ecological modelling projects that synthesised both \<idealised norms and norms of practice, Pu et al., see other philosophy of sci refs\>.
This workflow is used to provide structure and content to the preregistration template.

@@

In order to address the disjuncture between the iterative nature of model development, and the single-use, deterministic preregistration template, we take an 'expanded view of preregistration', that fits with the concept of 'adaptive preregistration' proposed by \<Srivastava\>.
This view of preregistration breaks with the current model of preregistration, wherein the author writes a single deterministic preregistration containing a rule for every decision, and shifts from ideation, preregistration to execution of the plan.
Two features define adaptive preregistration.
It contains 'plans to deploy flexible strategies' \<Srivastava\> wherein the author can supply a heuristic consisting of multiple different analysis or modelling strategies whose execution depends on the outcome of previous decision-points or analyses.
Secondly, the preregistration may be iterative and consist of interim preregistrations that mark phases of modelling and analysis as different parts of the data are observed \<Srivastava\>.
Thus, as the modeller proceeds through the model development process, the researcher can shift from ideation, preregistration, execution of the analysis and back to ideation and preregistration again, depending on the observed outcomes as each interim preregistration is executed \<Link to Figure, GitHub as a platform for adaptive preregistration, \<x-scrivener-item:///Users/egould/Dropbox/Apps/Scrivener/PhD_thesis.scriv?i
d=32FCFBDA-7CEE-4FD9-B8DD-F3073309C0D0\>\>.

@@

Before shifting from planning to the execution of the interim preregistration, each complete response in the interim preregistration should have a corresponding *GitHub issue* created (Figure X, step 3, document).
\<define GitHub issue, <https://guides.github.com/features/issues/>\>.
Relevant discussion between analysts about how to proceed with the intended analysis or interpreting preliminary results are tracked within an *issue*'s thread.
Each issue is assigned a unique number.
Any code or analysis outputs, such as figures, tables or other files, should be committed and tagged with the issue number, so that all analysis addressing that task is tracked within the *issue's* thread (Fig X, step 4, Do) \<screen-cap?\>
.
The URL for the GitHub issue should then be added to the relevant preregistration item, the preregistration document should then be committed with the changes, and the version number of the preregistration updated in a new *release*.

### 2023-09-27 _analysis/PRT-Appendix-1.Rmd
rename _analysis

---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: ELise Gould 
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

>>>>

---
title: "PRT Appendix - 1"
date: "`r Sys.Date()`"
output: github_document
---

Table specifying phases, steps, and item inclusion with justifications from workshop and literature in support.

@@

```{r session-info, echo = TRUE, eval = TRUE}
sessionInfo()
```
